\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{enumitem}
\title{Agentic AI Fleet Management Assistant\\End-Sem Project Report}
\author{Your Name}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
This report presents an agentic AI fleet management assistant that autonomously analyzes vehicle maintenance risks, retrieves guideline evidence using retrieval-augmented generation (RAG), and generates structured servicing recommendations. The system uses a LangGraph workflow with explicit state transitions and provides a modern deployable user interface.
\end{abstract}

\section{Problem Statement}
Fleet operators require timely maintenance decisions across many vehicles. Manual decision-making can miss safety-critical patterns. The objective is to build an assistant that reasons over fleet health, aligns recommendations with maintenance references, and produces auditable structured outputs.

\section{System Design}
\subsection{Input-Output Specification}
\textbf{Input:} Fleet data table and maintenance query.\\
\textbf{Output:} Health summary, prioritized action plan, retrieved sources, and operational disclaimer.

\subsection{Architecture}
The workflow consists of three nodes:
\begin{enumerate}[noitemsep]
    \item Risk analysis node (deterministic scoring)
    \item RAG retrieval node (Chroma vector search over guideline corpus)
    \item Recommendation node (structured generation with safety constraints)
\end{enumerate}

\section{Agentic Workflow and State}
State variables include vehicle features, risk analysis results, retrieved guidelines, reasoning trace, and final recommendation object. This explicit state allows traceable planning and robust debugging.

\section{RAG Pipeline}
Guidelines are chunked, embedded, and indexed in Chroma. At inference time, the system retrieves top-k relevant chunks based on the maintenance query and uses these as grounding context for recommendations.

\section{Hallucination Mitigation}
\begin{itemize}[noitemsep]
    \item Retrieval-grounded recommendation context
    \item Structured schema output to constrain claims
    \item Conservative fallback strategy when API or evidence is limited
    \item Mandatory safety disclaimer for responsible AI operation
\end{itemize}

\section{Results and Discussion}
Include:
\begin{itemize}
    \item Qualitative examples of recommendations for high-risk vehicles
    \item Comparative observations across different fleet conditions
    \item Failure modes (missing data, out-of-range telemetry) and handling
\end{itemize}

\section{Deployment}
The application is packaged for Streamlit deployment (Share Streamlit or Hugging Face Spaces). Public hosting link should be included in final submission.

\section{Conclusion}
The project demonstrates an end-to-end agentic AI assistant for practical fleet maintenance planning with explainable stateful reasoning and deployment-ready UX.

\end{document}
